% === Exercise 8.3.7 ===
\begin{Exercise}
\begin{enumerate}[a)]
\item
\begin{proof}
Suppose $A\cup B$ is $\mathbf{not}$ connected. i.e., there exists nonempty sets $U$, $V$ are relatively open in $A\cup B$ such that $U\cap V=\phi$ and $U\cup V=A\cup B$.
\begin{enumerate}
\item [$\mathbf{Case\ 1.}$] 
$A\cap U\neq \phi$ and $B\cap V\neq \phi$.

\vspace{1ex}

Set $U' := A\cap U$ and $V' := A\cap V$. We claim $U'$ and $V'$ separate $A\cup B$. \\
Consider $U'\cap V' = (A\cap U)\cap (A\cap V) = A\cap (U\cap V) = A\cap \phi = \phi.$
Then since $U$ is relatively open in $A\cup B$, there exists an open set $G$ such that $U = (A\cup B)\cap G$. Moreover, 
$$
U'
= A\cap U
= A\left( (A\cup B)\cap G \right)
= A\cap G.
$$
Hence $U'$ is relatively open in $A$ so is $V'$ with a similar argument.
Finally, we verify
$$
U'\cup V'
= (A\cap U)\cup(A\cap V)
= A\cap (U\cup V)
= A\cap (A\cup B)
= A.
$$
By definition, we conclude $U'$ and $V'$ separate $A$ which implies $A$ is not connected. This leads to a contradiction with hypothesis that $A$ is connected.

\item [$\mathbf{Case\ 2.}$]
$A\cap U = \phi$ or $B\cap V = \phi$.

\vspace{1ex}

W.L.O.G., we assume $A\cap U = \phi$. Consider
\begin{alignat*}{7}
\quad&& A\cup B &= U\cup V \\
\implies&& U\cap(A\cup B) &= U\cap(U\cup V) \\
\implies&& (U\cap A)\cup (U\cap B) &= U \\
\implies&& \phi\cup(U\cap) &= U \\
\implies&& U\cap B &= U \\
\implies&& U &\subseteq B.
\end{alignat*}
Set $B_1 := B\cap U$ and $B_2 := B\cap V$.
We consider
\begin{align*}
B_1\cup B_2
&= (B\cap U) \cup (B\cap V) \\
&= B\cap(U\cup U) \\
&= B\cap(A\cup B) \\
&= B.
\end{align*}
Moreover, with a similar argument from $\mathbf{Case\ 1.}$, we also know $B_1$ and $B_2$ are relatively open in $B$. By the way, $U = U\cap B = B_1 \neq \phi$. Then we should discuss whether $B_2 = \phi$ or not.

If $B_2 \neq \phi$, then since $B_2 = B\cap V$, we claim $B_1$ and $B_2$ separate $B$ by definition.
Otherwise $B_2 = \phi$, then continue to consider
\begin{alignat*}{7}
\quad&& A\cup B &= U\cup V \\
\implies&& A\cap(A\cup B) &= A\cap(U\cup V) \\
\implies&& A &= (A\cap U)\cup (A\cap V) \\
\implies&& A &= A\cap V \\
\implies&& A &\subseteq V.
\end{alignat*}
Since $B\cap V = \phi$ implies $V \subseteq B^c$, so $A \subseteq B^c$. We conclude $A\cap B = \phi$ which leads to a contradiction with hypothesis that $A\cap B\neq \phi$.

A similar argument proves the condition $B\cap V = \phi$. 
\end{enumerate}
Finally, we conclude $A\cap B$ is connected under the hypothesis as promised.
\end{proof}

\item
\begin{proof}
Denote $$E_k := \bigcup_{i=1}^{k}E_{n_i}.$$
where $n_i\in A \mbox{ for } i=1,2,\cdots,k$.
We pick $n_1\in A$ arbitrarily, then $E_1 = E_{n_1}$ is connected by hypothesis.

Assume for $n=k$, $E_k$ is connected. Then for $n=k+1$, we
pick $n_{k+1}\in A$ arbitrarily, then we know $E_k$ and $E_{n_{k+1}}$ are connected sets. Since $\cap_{\alpha\in A}E_{\alpha} \neq \phi$, it follows that $E_k \cap E_{n_{k+1}} \neq \phi$. From part a), we have $E_k \cup E_{n_{k+1}} = E_{k+1}$ is also connected.
By induction, we know $E_k$ is connected for all $k\in\mathbb{N}$ which implies
$$
E = \bigcup_{\alpha\in A} E_{\alpha}
$$ is connected.
\end{proof}

\item
\begin{proof}
Since a subset of $\mathbb{R}$ is connected if and only if $E$ is an interval, we suppose $A = [a_1, b_1]$ and $B = [a_2, b_2]$. Since $A\cap B \neq \phi$, we discuss all conditions which are fulfilled.
\begin{enumerate}
\item [$\mathbf{Case\ 1.}$]
$a_1 \leq b_1$ and $b_1 \leq a_2 < b_2$

where $A\cap B = [b1, a2] \neq \phi$. Then $A\cup B = [a_1, b_2]$ is an interval, so is connected.

\item [$\mathbf{Case\ 2.}$]
$a_1 \leq b_1$ and $a_2 \geq b_2$.

where $A\cap B = [b1, b2] \neq \phi$. Then $A\cup B = [a_1, a_2]$ is an interval, so is connected.

\item [$\mathbf{Case\ 3.}$]
$b_1 \leq a_1$ and $a_1 \leq b_2 < a_2$.

where $A\cap B = [a1, b2] \neq \phi$. Then $A\cup B = [b_1, a_2]$ is an interval, so is connected.

\item [$\mathbf{Case\ 4.}$]
$b_1 \leq a_1$ and $b_2 \geq a_2$.

where $A\cap B = [a1, a2] \neq \phi$. Then $A\cup B = [b_1, b_2]$ is an interval, so is connected.
\end{enumerate}
Hence, $A\cap B$ is always connected as promised.
\end{proof}

\item
\begin{proof}
The counter-example is that two subsets of $\mathbb{R}^2$ are supposed as following, 
\begin{align*}
A &:= \{(x,y) : -1\leq x \leq 1, -|x| \leq y \leq |x|\} \\
B &:=\{(x,y) : -1 \leq x \leq 1, -1 \leq y \leq 1\}\backslash\{(0,0)\}
\end{align*}
where $A\cap B = \{(x, y): -1 \leq x \leq 1, -|x| \leq y \leq |x|\} \backslash \{(0,0)\} \neq \phi.$

We can pick $U := \{(x,y):x<0\}$ and $V := \{(x,y):x>0\}$ to separate $A\cap B$, so $A\cap B$ is not connected.
\end{proof}

\end{enumerate}
\end{Exercise}